### 2016-12-13 BF_correctness.tex
continuing my pass...

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:bf-correctness}]
We use a game playing argument; please refer to
Figures~\ref{fig:bf-correctness-games1}
and~\ref{fig:bf-correctness-games2}. In game $\game{0}$, the
$\HashOracle$ oracle performs lazy sampling of elements from $[m]$
to mimic a random oracle (RO). For every distinct query,
$\HashOracle$ returns a random value sampled from $[m]$. It can be
seen that game $\game{0}$ exactly simulates the correctness game of
$\setprim_{\mathrm{Bloom}}$, and so
$\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) =
1}$.

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a$\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, x)$\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
if $x \not \in S$ then $\err \gets \err + 1$\\
Return 1\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, x)$\\
\nudge if $M[h_j] \neq 1$\\
\nudge \nudge Return $(0, (h_1, \ldots, h_j))$\\
if $x \not \in S$ then $\err \gets \err + 1$\\
Return~$(1, (h_1, \ldots, h_{k}) )$\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[h_j] \neq 1$ then \\
\nudge \nudge Return~$(0, (h_1, \ldots, h_{k}) )$\\
if $x \not \in S$ then $\err \gets \err +1$\\
Return~$(1, (h_1, \ldots, h_{k}) )$\\

@@

In $\game{3}$, we modify the $\HashOracle$ oracle so that on
query~$x$ it returns the~$k$ values that previously would have
required $k$ calls $\HashOracle(1,x), \ldots, \HashOracle(k,x)$. We
alter the $\TestOracle$ oracle accordingly, so that it makes a
single call to $\Hash$ rather than~$k$ such calls. (We assume that
$\Rep$ is also appropriately modified for the new behavior
of~$\HashOracle$.) We do this so we can assume that a
call~$\HashOracle(x)$ is pointless after a~$\TestOracle(x)$ call has
been made. This change results in the adversary getting $(k-1)$ hash
values ``for free,'' as we charge the adversary only for a single
query. \jnote{I don't see why we do this. The analysis is no easier,
but now the attacker gets free queries.}  It is obvious that
$\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.

%JK
Game~$\game{4}$ contains some important changes from
game~$\game{3}$. In $\game{4}$ the $\TestOracle$ oracle no longer
computes its answer directly, but instead refers to a
table~$\mathrm{Ans}[x]$ that is populated upon calls to the
$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is
undefined, $\TestOracle$ makes a call $\HashOracle(x)$; otherwise,
it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly
the values that~$\TestOracle(\qry_x)$ would have returned in the
previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes
the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$. It
maintains the table~$T$ because~$A$ is permitted to
call~$\HashOracle$ on $y \in S$.
%(We no longer need to maintain the table~$T$ because hash values are
%only determined by~$\HashOracle$ calls, and these are never repeated
%under our no-pointless-query assumption.)
It then computes the answer that~$\TestOracle(\qry_x)$ would return in
game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use
by~$\TestOracle$.
None of these changes alters the behavior of the game from the
adversary's perspective.

 but we will argue that $\Prob{\game{3}(A) = 1} \leq
\Prob{\game{4}(A)
  = 1}$.

At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
happens iff there are~$r$ calls to the $\HashOracle$ oracle that
increment~$\err$, i.e., queries $y \not\in S$ such that
$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
does not call~$\HashOracle$ on $y \in S$ because the indices
$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will
be \emph{independent} of those corresponding to any of the $y \in
S$. Thus these queries are wasted.  Now, there are at total of $q_T
+ q_H$ queries made to~$\HashOracle$, either directly by~$A$ or
indirectly by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to
return 1, there must be~$r$ among these that increment the counter.
We can assume without loss of generality that~$A$ halts as soon
as~$\err=r$ (which it can easily track), so there are
$\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query patterns to
consider.  As each error event is independent of all previous
choices made by the~$\HashOracle$, we need only consider the
probability of a single error. Using Kirsch and
Mitzenmacher's~\cite{kirsch2006less} upper bound on false positive
probability of a classical Bloom filter, we have
$\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k
+ O(1/n) \right)^r$. To summarize,
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
which is the bound claimed in the theorem statement.
\begin{figure}[tp]
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{4}(A)$} \\ %\fbox{$\game{5}(A)$}}\\
$S \getsr A$; $\err \gets 0$;  $\calC \gets \emptyset$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
%if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(\qry_y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
%\nudge $c \gets c + 1$\\
%\nudge for $j \in \{1,2,\ldots,k\}$\\
%\nudge $v_j \getsr [m]$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
%\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge $\Break$\\
if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
%if $c \notin \calI$ then $\bad \gets \true$\\
if $y \not\in S$ then $\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Game $\game{4}$ for the
proof of Theorem~\ref{thm:bf-correctness}.}
\label{fig:bf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}

>>>>

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:bf-correctness}]
We use a game playing argument; please refer to
Figures~\ref{fig:bf-correctness-games1}
and~\ref{fig:bf-correctness-games2}. In game $\game{0}$, the
$\HashOracle$ oracle performs lazy sampling of elements from $[m]$
to mimic a random oracle. For every distinct query, $\HashOracle$
returns a random value sampled from $[m]$. It can be seen that game
$\game{0}$ exactly simulates the correctness game of
$\setprim_{\mathrm{Bloom}}$, and so
$\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) =
1}$.

@@

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a$\\

@@

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, x)$\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
if $x \not \in S$ then $\err \gets \err + 1$\\
Return 1\\

@@

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j, x)$\\
\nudge if $M[h_j] \neq 1$\\
\nudge \nudge Return $(0, (h_1, \ldots, h_j))$\\
if $x \not \in S$ then $\err \gets \err + 1$\\
Return~$(1, (h_1, \ldots, h_{k}) )$\\

@@

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[h_j] \neq 1$ then \\
\nudge \nudge Return~$(0, (h_1, \ldots, h_{k}) )$\\
if $x \not \in S$ then $\err \gets \err +1$\\
Return~$(1, (h_1, \ldots, h_{k}) )$\\

@@

In $\game{3}$, we modify the $\HashOracle$ oracle so that on
query~$x$ it returns the~$k$ values that previously would have
required $k$ calls $\HashOracle(1,x), \ldots, \HashOracle(k,x)$. We
alter the $\TestOracle$ oracle accordingly, so that it makes a
single call to $\Hash$ rather than~$k$ such calls. (We assume that
$\Rep$ is also appropriately modified for the new behavior
of~$\HashOracle$.) We do this so we can assume that a
call~$\HashOracle(x)$ is pointless after a~$\TestOracle(x)$ call has
been made. This change results in the adversary getting $(k-1)$ hash
values ``for free,'' as we charge the adversary only for a single
query. \jnote{Can we do better by being more careful?} It is obvious
that $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.

Game~$\game{4}$ contains some important changes from
game~$\game{3}$. In $\game{4}$ the $\TestOracle$ oracle no longer
computes its answer directly, but instead refers to a
table~$\mathrm{Ans}[x]$ that is populated upon calls to the
$\HashOracle$ oracle.  If $\mathrm{Ans}[x]$ is undefined,
$\TestOracle$ makes a call $\HashOracle(x)$; otherwise, it returns
the contents of~$\mathrm{Ans}[x]$, which contains exactly the values
that~$\TestOracle(q_x)$ would have returned in the previous game.
The $\HashOracle$ oracle, on input~$x$, computes
values~$v_1,\ldots,v_k$ as in $\game{3}$. %It maintains the table~$T$
%because~$A$ is permitted to call~$\HashOracle$ on $y \in S$.
%(We no longer need to maintain the table~$T$ because hash values are
%only determined by~$\HashOracle$ calls, and these are never repeated
%under our no-pointless-query assumption.)
It then computes the answer that~$\TestOracle(q_x)$ would return in
game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use
by~$\TestOracle$. None of these changes alters the view of~$A$, and
so $\Prob{\game{3}(A) = 1} = \Prob{\game{4}(A)
  = 1}$. \jnote{You had $\leq$ before.}

Note that $\game{4}(A)=1$ iff there are~$r$ queries to the
$\HashOracle$ oracle that increment~$\err$, i.e., queries $y \not\in
S$ such that $\bigwedge_{j=1}^{k} M[v_j]=1$.
%We can assume without
%loss of generality that~$A$ does not call~$\HashOracle$ on $y \in S$
%because the indices $v_1,v_2,\ldots,v_k$ that will correspond to any
%$y \not\in S$ will be \emph{independent} of those corresponding to
%any of the $y \in S$. Thus these queries are wasted.
There are at total of $q_T + q_H$ queries made to~$\HashOracle$,
either directly by~$A$ or indirectly when~$A$ calls~$\TestOracle$.
For $\game{4}(A)$ to return~1, there must be~$r$ among these that
increment~$\err$. %We can assume without loss of generality that~$A$
%halts as soon as~$\err=r$ (which it can easily track), so
There are $\binom{q_T+q_H}{r}$ possible ``winning'' query patterns
to consider.  \jnote{I changed the bound; I don't think it was
correct before.} As each error event is independent of all previous
choices made by the~$\HashOracle$, we need only consider the
probability of a single error. Using the upper bound on false
positives for the classical Bloom filter shown by Kirsch and
Mitzenmacher~\cite{kirsch2006less}, we have $\Prob{\game{4}(A)=1}
\leq \binom{q_T+q_H}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
We conclude that
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,,
\]
as claimed.
\begin{figure}[tp]
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{4}(A)$} \\ %\fbox{$\game{5}(A)$}}\\
$S \getsr A$; $\err \gets 0$;  $\calC \gets \emptyset$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
%if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
%\nudge $c \gets c + 1$\\
%\nudge for $j \in \{1,2,\ldots,k\}$\\
%\nudge $v_j \getsr [m]$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
%\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge Return $\left(v_1,\ldots,v_k\right)$\\
%\nudge \nudge $\Break$\\
%if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
%if $c \notin \calI$ then $\bad \gets \true$\\
if $y \not\in S$ then $\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Game $\game{4}$ for the
proof of Theorem~\ref{thm:bf-correctness}.}
\label{fig:bf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}

### 2016-12-13 ds-correctness.tex
continuing my pass...

\begin{proof}[Theorem~\ref{thm:ds-correctness}]
%\fixme{Animesh: remove these Cref things and replace with references
  %like I have them in the text.}
We use a game playing argument to prove this theorem. Please refer to
Figure~\ref{fig:ds-correctness-games}. In game \game{0} adversary $A$ attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
\begin{equation}
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} = \Prob{\game{0}(A)=1}
\end{equation}

In game $\game{1}$, $A$ attacks a related data structure $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function. Let $B$ be a prf-adversary as shown in Figure~\ref{fig:ds-correctness-adv}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
\begin{align*}
\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\
\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}
\end{align*}

By a standard conditioning of PRF advantage, we have
\begin{equation*}
\Prob{\game{0}(A)=1} = \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}%\label{eq:13}
\end{equation*}

Coming back to the game playing argument, in game $\game{2}$, $\HashOracle$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries. In addition, the $\Test$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\Test$. It also sets a boolean $\bad$ flag to $\false$ if queries which are not indexed by the $r$-set $\calI$ are false-positives, and queries indexed by set $\calI$ are not false-positives. It must be noted that $\bad$ does not affect the output of the $\Test$ or the game. We argue that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$. Game $\game{3}$ is identical to $\game{2}$, except it returns 0 if $\bad$ is set to $\true$. $\game{3}$ returns 1 whenever $\game{2}$ would return 1, and $\bad$ remained false in $\game{2}$. So, basically $\game{3}$ guessed exactly the $r$ queries that results in errors. Hence, $\Prob{\game{3}(A)=1} = \frac{1}{\binom{q}{r}}\Prob{\game{2}(A)=1}$.

Let $D$ be an adversary shown in Figure~\ref{fig:lin-correctness-zq-adv}. It effectively simulates game~$game{3}$, guessing which~$r$ of~$A$'s queries to send to its own~$\TestOracle$. By its construction, if $\game{3}(A)=1$ then~$D$ will also find~$r$ errors in~$\tilde{\setprim}_{\mathrm{ds}}$.  Thus, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}$.

It can be easily seen that  $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature. So, for an adversary $D$ and $r=1$, advantage of $D$ to win $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper bounded by the false-positive probability of a classical Bloom filter. For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$. Also, since $\HashOracle$ in $\game{3}$ returns $k$ random values for each query, the event of getting a false positive is independent of the index of the query. So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\binom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$

\noindent
To summarize, we have
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed

@@

\medskip
\oracle{$\HashOracle(x)$}\\
for $j = 1$ to~$k$\\
\nudge $v_j \getsr [m]$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{3}$ for the
proof of Theorem~\ref{thm:ds-correctness}.}
\label{fig:ds-correctness-games}

\end{figure}

%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$
\begin{figure}
\centering
\fpage{.8}{
\hpagessl{.5}{.45}
{
$\adversaryv{B^{\calO}}$\\
$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup \{x\}$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1

\medskip
\oracle{$\HashOracle(x)$}\\
\nudge Return $\OK$, for $j\in[1,k]$
}
{
$\adversaryv{D^\TestOracle}$\\[4pt]
On input $\emptystring$:\\
\nudge $S \getsr A$\\
\nudge Return~$S$\\
On input $\pubaux$:\\
\nudge $c \gets 0$, $\calC \gets \emptyset$, $\err \gets 0$\\
\nudge $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
\nudge Run $A(\pubaux)$\\
\nudge When $A$ asks $\qry_x$:\\
\nudge\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge\nudge $\calC \gets \calC \cup \{x\}$\\
\nudge\nudge $c \gets c+1$; $r \gets 0$\\
\nudge\nudge if $c \in \mathcal{I}$\\
\nudge\nudge \nudge $r \gets \TestOracle(\qry_x)$\\
\nudge\nudge Reply to~$A$ with $r$\\
\nudge When $A$ halts:\\
\nudge\nudge Return $\bot$
}
}
\caption{Left: Adversary $B$ simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for Theorems~\ref{thm:ds-correctness} }\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
\end{figure}

\end{proof}

>>>>

\begin{proof} \jnote{I did not check this proof; see my comment before the proof.}
We use a game-playing argument to prove this theorem. Please refer to
Figure~\ref{fig:ds-correctness-games}. In game \game{0} adversary $A$ attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
\begin{equation}
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} = \Prob{\game{0}(A)=1}
\end{equation}

@@

\medskip
\oracle{$\HashOracle(x)$}\\
for $j = 1$ to~$k$\\
\nudge $v_j \getsr [m]$\\
Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Games
$\game{0}$--$\game{3}$ for the proof of
Theorem~\ref{thm:ds-correctness}.} \label{fig:ds-correctness-games}
\end{figure}

In game $\game{1}$, $A$ attacks a related data structure
$\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a
random function. Let $B$ be a prf-adversary as shown in
Figure~\ref{fig:ds-correctness-adv}. Based on its challenge bit $b$,
it exactly simulates $\game{0}$ or $\game{1}$. So,
\begin{align*}
\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\
\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}
\end{align*}
By a standard argument, we have
\begin{equation*}
\Prob{\game{0}(A)=1} = \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}.%\label{eq:13}
\end{equation*}

In game $\game{2}$, $\HashOracle$ returns random values sampled from
$[m]$, assuming $A$ makes no pointless queries. In addition, the
$\TestOracle$ oracle keeps a counter, $c$ to keep track of the
number of queries by $A$ to the $\TestOracle$. It also sets a
boolean $\bad$ flag to $\false$ if queries which are not indexed by
the $r$-set $\calI$ are false-positives, and queries indexed by set
$\calI$ are not false-positives. It must be noted that $\bad$ does
not affect the output of the $\TestOracle$ or the game. We argue
that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$. Game
$\game{3}$ is identical to $\game{2}$, except it returns 0 if $\bad$
is set to $\true$. $\game{3}$ returns 1 whenever $\game{2}$ would
return 1, and $\bad$ remained false in $\game{2}$. So, basically
$\game{3}$ guessed exactly the $r$ queries that results in errors.
Hence, $\Prob{\game{3}(A)=1} =
\frac{1}{\binom{q}{r}}\Prob{\game{2}(A)=1}$.

Let $D$ be the adversary shown in
Figure~\ref{fig:lin-correctness-zq-adv}. It effectively simulates
game~$\game{3}$, guessing which~$r$ of~$A$'s queries to send to its
own~$\TestOracle$. By its construction, if $\game{3}(A)=1$ then~$D$
will also find~$r$ errors in~$\tilde{\setprim}_{\mathrm{ds}}$. Thus,
$\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =
\Prob{\game{3}(A) = 1}$.

%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$
\begin{figure}[htb]
\centering
\fpage{.8}{
\hpagessl{.5}{.45}
{
$\adversaryv{B^{\calO}}$\\
$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup \{x\}$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1

\medskip
\oracle{$\HashOracle(x)$}\\
\nudge Return $\OK$, for $j\in[1,k]$ } {
$\adversaryv{D^\TestOracle}$\\[4pt]
On input $\emptystring$:\\
\nudge $S \getsr A$\\
\nudge Return~$S$\\
On input $\pubaux$:\\
\nudge $c \gets 0$, $\calC \gets \emptyset$, $\err \gets 0$\\
\nudge $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
\nudge Run $A(\pubaux)$\\
\nudge When $A$ asks $\qry_x$:\\
\nudge\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge\nudge $\calC \gets \calC \cup \{x\}$\\
\nudge\nudge $c \gets c+1$; $r \gets 0$\\
\nudge\nudge if $c \in \mathcal{I}$\\
\nudge\nudge \nudge $r \gets \TestOracle(\qry_x)$\\
\nudge\nudge Reply to~$A$ with $r$\\
\nudge When $A$ halts:\\
\nudge\nudge Return $\bot$ } } \caption{Left: Adversary $B$
simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for
Theorem~\ref{thm:ds-correctness}.
}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
\end{figure}

It can be easily seen that $\tilde{\setprim}_{\mathrm{ds}}$ is the
scheme analyzed in the classical Bloom-filter literature. So, for an
adversary $D$ and $r=1$, advantage of $D$ to win
$\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper
bounded by the false-positive probability of a classical Bloom
filter. For $r > 1$, based on the assumption that $A$ makes no
pointless queries, the queries made by $A$ are distinct and not
elements of the original set $S$. Also, since $\HashOracle$ in
$\game{3}$ returns $k$ random values for each query, the event of
getting a false positive is independent of the index of the query.
So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =
{\binom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$. To
summarize, we have
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed
\end{proof}
